Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-18 paper/paper.tex
removed quick reference to a monte-carlo way of simulating that I now cant find Tested everything on quipu.

Variations of the Huang 2003 model that stochasticly account for
molecular interaction and
diffusion~\cite{kerr2006division,fange2006noise} and monte-carlo
simulations that implement this stochastic version of Huang's mean
field reaction rates \fixme{citation needed on the monte-carlo method}
confirm the major results obtained by Huang's model, and more
successfully predict experimentally observed oscillations in round
cell phenotypes~\cite{fange2006noise, huang2004min}. The successful
simulations of three pronged cells mentioned above are stochastic
simulations~\cite{varma2008min}. Biochemical models of broader scope
have also been used to study the MinD system and show consistent
results~\cite{arjunan2010new}.

>>>>

Variations of the Huang 2003 model that stochasticly account for
molecular interaction and
diffusion~\cite{kerr2006division,fange2006noise} confirm the major
results obtained by Huang's model, and more successfully predict
experimentally observed oscillations in round cell
phenotypes~\cite{fange2006noise, huang2004min}. The successful
simulations of three pronged cells mentioned above are stochastic
simulations~\cite{varma2008min}. Biochemical models of broader scope
have also been used to study the MinD system and show consistent
results~\cite{arjunan2010new}.
